---
output:
  word_document: default
  html_document: default
---
```{r}
#1/1
likelihoodGiven <- c( 0.91, 0.09)
likelihoodGivenNot <- c(0.16,0.84)

getDataFromLikelihood <- function( likelihood, numPointsDisease) 
{
	d <- vector(mode="integer", length=numPointsDisease);
	
	for( i in 1:numPointsDisease ) 
	{
		if( runif(1) <= likelihood[1] )
		{
			d[i] <- 1;
		}
		else
		{
			d[i] <- 2;
		}
			
	}
	
	return(d)
}

numTestsDisease <- 1:30
numSimulationsPerCycleDisease <- 1000

averagePosteriorValue <- c(length=length(numTestsDisease))
estimatedPowerDisease<- c(length=length(numTestsDisease))

for( i in numTestsDisease ) 
{
	posteriorValuesDisease <- c(length=numSimulationsPerCycleDisease)
		
	for( j in 1:numSimulationsPerCycleDisease  ) 
	{
		# reset our prior each time
		probDisease <-  c(0.01,0.9999)
	
		data <- getDataFromLikelihood( likelihoodGiven, numTestsDisease[i])
	
		for( k in 1:length(data))
		{
			denom <- probDisease[1] * likelihoodGiven[data[i]] + probDisease[2] * likelihoodGivenNot[data[k]];
	
			probDisease[1] = probDisease[1] * likelihoodGiven[data[k]] / denom;
			probDisease[2] = probDisease[2] * likelihoodGivenNot[data[k]] / denom;
		}
		
		posteriorValuesDisease[j] = probDisease[1]	
	}
	
	averagePosteriorValue[i] = mean(posteriorValuesDisease)
	estimatedPowerDisease[i] <- sum(posteriorValuesDisease >= 1-0.01  ) / numSimulationsPerCycleDisease 
}

plot(numTestsDisease,estimatedPowerDisease)
```

```{r}
#1/2
rm(list=ls())
likelihoodGiven <- c( 0.91, 0.09)
likelihoodGivenNot <- c(0.16,0.84)

getDataFromLikelihood <- function( likelihood, numPointsDisease) 
{
	d <- vector(mode="integer", length=numPointsDisease);
	
	for( i in 1:numPointsDisease ) 
	{
		if( runif(1) <= likelihood[2] )
		{
			d[i] <- 1;
		}
		else
		{
			d[i] <- 2;
		}
			
	}
	
	return(d)
}

numTestsDisease <- 1:20
numSimulationsPerCycleDisease <- 1000

averagePosteriorValue <- c(length=length(numTestsDisease))
estimatedPowerDisease<- c(length=length(numTestsDisease))

for( i in numTestsDisease ) 
{
	posteriorValuesDisease <- c(length=numSimulationsPerCycleDisease)
		
	for( j in 1:numSimulationsPerCycleDisease  ) 
	{
		# reset our prior each time
		probDisease <-  c(0.01,0.9999)
	
		data <- getDataFromLikelihood( likelihoodGiven, numTestsDisease[i])
	
		for( k in 1:length(data))
		{
			denom <- probDisease[2] * likelihoodGivenNot[data[i]] + probDisease[1] * likelihoodGiven[data[k]];
	
			probDisease[2] = probDisease[2] * likelihoodGivenNot[data[k]] / denom;
			probDisease[1] = probDisease[1] * likelihoodGiven[data[k]] / denom;
		}
		
		posteriorValuesDisease[j] = probDisease[2]	
	}
	
	averagePosteriorValue[i] = mean(posteriorValuesDisease)
	estimatedPowerDisease[i] <- sum(posteriorValuesDisease >= 1-0.01  ) / numSimulationsPerCycleDisease 
}

plot(numTestsDisease,estimatedPowerDisease)
```

#1/3: So for the number of test that you need if you test positive is 18, while the number of test needed if you test negative is 7. About 1000 people will test positive, while 999,000 people will test negative. I would say we weould need to budget for about $17 to $18 million for all the test that they plan to do for one year.


```{r}
#2/1
rm(list=ls())
likelihoodGiven <- c( 0.96, 0.04)
likelihoodGivenNot <- c(0.05,0.95)

getDataFromLikelihood <- function( likelihood, numPointsDisease) 
{
	d <- vector(mode="integer", length=numPointsDisease);
	
	for( i in 1:numPointsDisease ) 
	{
		if( runif(1) <= likelihood[1] )
		{
			d[i] <- 1;
		}
		else
		{
			d[i] <- 2;
		}
			
	}
	
	return(d)
}

numTestsDisease <- 1:10
numSimulationsPerCycleDisease <- 1000

averagePosteriorValue <- c(length=length(numTestsDisease))
estimatedPowerDisease<- c(length=length(numTestsDisease))

for( i in numTestsDisease ) 
{
	posteriorValuesDisease <- c(length=numSimulationsPerCycleDisease)
		
	for( j in 1:numSimulationsPerCycleDisease  ) 
	{
		# reset our prior each time
		probDisease <-  c(0.01,0.9999)
	
		data <- getDataFromLikelihood( likelihoodGiven, numTestsDisease[i])
	
		for( k in 1:length(data))
		{
			denom <- probDisease[1] * likelihoodGiven[data[i]] + probDisease[2] * likelihoodGivenNot[data[k]];
	
			probDisease[1] = probDisease[1] * likelihoodGiven[data[k]] / denom;
			probDisease[2] = probDisease[2] * likelihoodGivenNot[data[k]] / denom;
		}
		
		posteriorValuesDisease[j] = probDisease[1]	
	}
	
	averagePosteriorValue[i] = mean(posteriorValuesDisease)
	estimatedPowerDisease[i] <- sum(posteriorValuesDisease >= 1-0.01  ) / numSimulationsPerCycleDisease 
}

plot(numTestsDisease,estimatedPowerDisease)
```

```{r}
#2/1
rm(list=ls())
likelihoodGiven <- c( 0.96, 0.04)
likelihoodGivenNot <- c(0.05,0.95)

getDataFromLikelihood <- function( likelihood, numPointsDisease) 
{
	d <- vector(mode="integer", length=numPointsDisease);
	
	for( i in 1:numPointsDisease ) 
	{
		if( runif(1) <= likelihood[2] )
		{
			d[i] <- 1;
		}
		else
		{
			d[i] <- 2;
		}
			
	}
	
	return(d)
}

numTestsDisease <- 1:10
numSimulationsPerCycleDisease <- 1000

averagePosteriorValue <- c(length=length(numTestsDisease))
estimatedPowerDisease<- c(length=length(numTestsDisease))

for( i in numTestsDisease ) 
{
	posteriorValuesDisease <- c(length=numSimulationsPerCycleDisease)
		
	for( j in 1:numSimulationsPerCycleDisease  ) 
	{
		# reset our prior each time
		probDisease <-  c(0.01,0.9999)
	
		data <- getDataFromLikelihood( likelihoodGiven, numTestsDisease[i])
	
		for( k in 1:length(data))
		{
			denom <- probDisease[2] * likelihoodGivenNot[data[i]] + probDisease[1] * likelihoodGiven[data[k]];
	
			probDisease[2] = probDisease[2] * likelihoodGivenNot[data[k]] / denom;
			probDisease[1] = probDisease[1] * likelihoodGiven[data[k]] / denom;
		}
		
		posteriorValuesDisease[j] = probDisease[2]	
	}
	
	averagePosteriorValue[i] = mean(posteriorValuesDisease)
	estimatedPowerDisease[i] <- sum(posteriorValuesDisease >= 1-0.01  ) / numSimulationsPerCycleDisease 
}

plot(numTestsDisease,estimatedPowerDisease)
```

#2/2: So for the number of test that you need if you test positive is 6, while the number of test needed if you test negative is 4. About 1000 people will test positive, while 999,000 people will test negative. If the test cost $2 each then it would be about the same amount to budget for if the test were $1 each. 